\setcounter{page}{1}
\renewcommand{\abstractname}{Abstract}
\begin{abstract}
The Southwestern University of Finance and Economics (SWUFE) is a top university specialized in finance, economics, and business. It is known for its entrepreurial character and unremitting endeavours to address the needs of the people and society through academics, research, and influence on alumni, drawn from the legacy of its founders and generations of excellent alumni.

SWUFE is located in Chengdu, the engine-city for the development of Western China and the fourth-largest aviation hub in China.

The university traces its origin back to the year of 1925, when a group of students and academics from St. John's University in Shanghai, led by the prominent scholar Zhang Shouyong, left the school and founded the Kwang Hua University (Guanghua University) in Shanghai. In 1938, following the outbreak of the Second Sino-Japanese War, the university relocated its headquarters to Chengdu. This move was mirrored by other major universities in the east of China who relocated their operations to Western China during that time. In 1946, the Chengdu branch of Kwang Hua University formed an independent private univesity called Chenghua University.

After 1952, the university became a public school and was renamed and restructured several times until it received its current name, Southwestern University of Finance and Economics (SWUFE), in 1985. In 1995, SWUFE became a Project 211 University, in 2011, SWUFE was listed as 985 Innovative Platform for Key Disciplines Project University.

\noindent{\textbf{Keywords: }SWUFE; LaTeX; Python}
\end{abstract}